DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-28 paper/background.tex
Change figure sizes
Many of the figures were relatively small and hard to see, so the sizes
were increased.
Add Minje's part

\section{Background and Related Work} \label{sec:background}

In this section, we provide background and related work on the
application of deep learning in robotics, particularly autonomous
vehicles.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/endtoend_redrawn}
  \caption{Standard robotics control vs. DNN based end-to-end
    control. Adopted from ~\cite{Levine2017cs294}.}
  \label{fig:end-to-end-control}
\end{figure}

@@

\subsection{Embedded Computing Platforms for Real-Time Inferencing}
Real-time embedded systems, such as an autonomous vehicle, present
unique challenges for deep learning, as the computing platforms of such
systems must satisfy two often conflicting goals~\cite{Otterness2017}:
%% Recent successes in AI, including NVIDIA's DAVE-2 showing, are due
%% in large part to the increased computing performance,
%% which afforded researchers to train and use ever deeper neural networks with
%% high accuracy.
%% For practical applications, the computer platform in an
%% autonomous vehicle must satisfy two often conflicting goals:
The platform must provide 
enough computing capacity for real-time processing of computationally
expensive AI workloads (deep neural networks);
The platform must also satisfy various
constraints such as cost, size, weight, and power consumption limits.

@@

The primary objectives of this study are to understand (1) the
necessary computing performance for applying AI technology-based
robotics systems, and (2) what kind of computing architecture and
runtime supports are most appropriate for such workload. To
achieve these goals, we implement a low-cost autonomous car platform
as a case-study and systematically conduct experiments, which we will 
describe in the subsequent sections.

>>>>

\section{Background} \label{sec:background}

In this section, we provide background on the application of deep
learning in robotics, particularly autonomous vehicles.

\subsection{Deep Convolutional Neural Network}
\fixme{CNN background}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.75\textwidth]{figs/endtoend_redrawn}
  \caption{Standard robotics control vs. DNN based end-to-end
    control. Adopted from ~\cite{Levine2017cs294}.}
  \label{fig:end-to-end-control}
\end{figure}

@@

\subsection{Embedded Computing Platforms for Real-Time Inferencing}
\fixme{we can consider moving this section to a dedicated related work
  section at the end.}
Real-time embedded systems, such as an autonomous vehicle, present
unique challenges for deep learning, as the computing platforms of such
systems must satisfy two often conflicting goals~\cite{Otterness2017}:
%% Recent successes in AI, including NVIDIA's DAVE-2 showing, are due
%% in large part to the increased computing performance,
%% which afforded researchers to train and use ever deeper neural networks with
%% high accuracy.
%% For practical applications, the computer platform in an
%% autonomous vehicle must satisfy two often conflicting goals:
The platform must provide 
enough computing capacity for real-time processing of computationally
expensive AI workloads (deep neural networks);
The platform must also satisfy various
constraints such as cost, size, weight, and power consumption limits.

@@

The \emph{primary objectives of this study} are to understand (1) the
necessary computing performance for applying AI technology-based
robotics systems, and (2) what kind of computing architecture and
runtime supports are most appropriate for such workload. To
achieve these goals, we implement a low-cost autonomous car platform
as a case-study and systematically conduct experiments, which we will 
describe in the subsequent sections.

### 2018-01-28 paper/related.tex
Added DonkeyCar to related works as footnote
Add Minje's part

\section{Related Work}\label{sec:related}

Autonomous vehicles are becoming an increasingly interesting research topic as computing platforms capable of safely processing sensor input into safe vehicle controls become smaller and more affordable.  The model proposed in End-To-End Learning for Self-Driving Cars \cite{Bojarski2016} is viable on a platform as simple as a Raspberry Pi.

Given smaller, affordable platforms with multiple cores and even GPU based parallel processing such as the Tegra X1 \cite{NVIDIA2015} and the recently released Tegra X2 \cite{Amert2017}, allocation and management of available shared CPU and GPU resources \cite{Kim2016} becomes increasingly important.  Research on improving the performance of neural networks \cite{Jouppi2017} also attributes to the viability of using these models in small systems.

Together with hardware and platform improvements, there have been significant improvements in the algorithms such as a neural network algorithm capable of surpassing human level control at atari games \cite{DBLP}.  A popular technique had been to take sensor input and determine a depth map, such as the model used in \cite{Michels:2005}. End-to-end models such as the one used in \cite{Bojarski2016} can improve the efficiency of the model.  Improving the flexibility of the model and it abilty to adapt to different situations and avoiding overfitting to training data continues to be an important topic in autonomous driving \cite{Pomerleau1989}.

Producing large platforms such as DAVE \cite{LeCun:04} has often been the approach to developing the technology for self-driving vehicles.  This approach, while certainly effective, presents a higher barrier to entry for research groups.  Smaller, more focused platforms, such as the one found in \cite{Michels:2005} present a more accesible way forward.

>>>>

\section{Related Work}
% discusstion
% - model is still quite small. cam we use bigger CNNs?
\fixme{What we want to say:
  1) We showed DNN is feasible on today's embedded computing
  platforms.
  2) But, the CNN model is rather smaller-kind with respect to today's
  state-of-the-art CNNs, which are much bigger.
  3) show table, borrowed from google's object detection api
  paper~\cite{huang2017speed}. 
  4) Applying these much more complex DNNs would improve network accuracy
  but they are obviously challenging for embedded computing
  platforms. We already discussed computing platform improvement that
  improve performance of executing a given DNN workload in
  section 2, so here we discuss model compression that reduces
  the necessary computing load itself.}

% related work on efficient DNN representation and processing.
While repeated feedforward and backpropagation operations during
the training time account for most of the computational cost in
deep learning, there is a growing need for an improved efficiency
during the inferencing time as well, especially because of the
potential of utilizing Deep Neural Networks (DNN) for the real-time
pattern recognition tasks in embedded systems, as our paper
exemplifies.

When a DNN is deployed in those implementations with limited
resources, such as memory and power, the floating-point operations
involved in the large matrix multiplications are a burdensome task.
Many recent advances in network compression showed promising results
in reducing such computational cost during the feedforward
process. The fundamental assumption in those techniques is that the
DNNs are redundant in their structure and representation. For example,
network pruning can thin out the network and provides a more condensed
topology~\cite{han2015deep}.
Another common compression method is to reduce the
quantization level of the network parameters, so that arithmetic
defined with the floating-point operations are replaced with low-bit
fixed-point counterparts. To this end, single bit quantization of the
network parameters or ternary quantization have been recently proposed
~\cite{hwang2014fixed,soudry2014expectation,kim2016bitwise,rastegari2016xnor,hubara2016binarized,beauchamp2006embedded,govindu2004analysis}.
In those networks, the inner product between the
originally real-valued parameter vectors is defined with XNOR followed
by bit counting, so that the network can greatly minimize the
computational cost in the hardware implementations. This drastic
quantization can produce some additional performance loss, but those
new binarized or ternarized systems provide a simple quantization
noise injection mechanism during training so that the additional error
is minimized to an acceptable level.

The XNOR operation and bit counting have been known to be efficient in
hardware implementations. In~\cite{rastegari2016xnor}, it was shown
that the binarized convolution can substitute the expensive
convolutional feedforward operations in a regular Convolutional Neural
Network (CNN), %% by using only about 1.5\% of the memory space, while
providing 20 to 60 times faster feedforward. Binary weights were also
able to provide 7 times faster feedforward than a floating-point
network for the hand written digit recognition task as well as 23
times faster matrix multiplication tasks on
GPU~\cite{hubara2016binarized}.
Moreover, FPGA implementations showed that the XNOR operation is 200
times cheaper than floating-point multiplications with 
single precision~\cite{beauchamp2006embedded,govindu2004analysis}.
XNOR-POP is another hardware implementation that reduced
the energy consumption of a CNN by 98.7\%~\cite{jiang2017xnor}.

% related work on testbeds
\fixme{discuss MIT racecar, UPENN car, donkey car and other testbeds?
  The points of discussion may include: 1) they are expensive. 2)
  donkey car is similar to us, but still a bit more expnsive, and more
  importantly there is no existing studies which systematically evaluate
  real-time performance of using DNN on embedded computing
  platforms. Our work provides quantitive real-time performance
  evaluation results, using a known DNN used in a real self-driving
  car. Our work is fully reproducible at a very low cost, lowring the
  barrier to entry in researching self-driving cars, helping the
  community blah blah blah.}
